Second-Generation Web Interface to Correcting ASR Output

### 2018-05-21 2018-ftc-vancouver/webapp.tex
spelling errors as pointed out by reviewer

The best widespread match to our task is that of creating an application for
transcribing speech recordings. Let's compare the two tasks, pointing out the
main points of difference. For reference, we take (1)
Transcriber\footnote{trans.sourceforge.net}, a classical open-source program
written in TCL, (2) oTranscribe\footnote{otranscribe.com}, a free modern
web-based transcription tool and (3) Transcribe\footnote{transcribe.wreally.com}
a commercial web-based transcription tool.

@@

Legend to Figure~\ref{fig:scn1lab}:
\begin{enumerate}
\item{
    Header with
    \begin{itemize}
    \item{app name linking to start page,}
    \item{about link,}
    \item{search field and}
    \item{username input field;}
    \end{itemize}
}
\item{Identifier of the recording;}
\item{Automatically transcribed segments in grey;}
\item{Manually transcribed segments in black;}
\item{Currently played-back word highlighted by yellow background;}
\item{Marked word highlighted in regent st. blue;}
\item{
    Marked word info:
    \begin{itemize}
    \item{
        occurrence: the word with contextual capitalization and
        punctuation as it appeard in the text (currently being edited as the
        selected initial letter reveals),
    }
    \item{form: normalized word form as it appears in the word list,}
    \item{pronunciation: Czech phonetic transcription of the word,}
    \item{
        position: time of the beginning of the word in seconds from the
        start of the recording;
    }
    \end{itemize}
}
\item{
    Tools for storing:
    \begin{itemize}
    \item{direct links to the audio files,}
    \item{selecting the whole transcription for easy pasting,}
    \item{storing the decoded recording in the browser's IndexedDB;}
    \end{itemize}
}
\item{Graphical equalizer for compensating narrow-band noise;}
\item{
    Audio playback controls:
    \begin{itemize}
    \item{play/pause button,}
    \item{current playback position,}
    \item{playback scrollbar,}
    \item{total recording length;}
    \end{itemize}
}
\item{Current position reflected in URL fragment.}
\end{enumerate}

@@

Legend to Figure~\ref{fig:scn2lab}:
\begin{enumerate}
\item{
    Selecting a text range with the mouse defines the segment the user is about
    to transcribe;
}
\item{
    The edit tool with
    \begin{itemize}
    \item{textarea prefilled with the current transcription,}
    \item{playback button that plays the corresponding segment,}
    \item{save button and}
    \item{download-segment button, which initiates a file-save action for the
    audio segment corresponding the the selected text. The synthesis of the
    downloaded file takes place in the browser.}
    \end{itemize}
}
\end{enumerate}

@@

Although this may not seem like a big deal, it does make affect the
responsiveness and memory footprint of the page.

@@

Wrapping the word would definetely be more robust and less error-prone but the
constant changes in the DOM during playback with possible frequent reflows speak
against it. Finding the exact position of each word and drawing a rectangle
precisely beneath it (beneath on the z-axis; over it in the x-y sense), avoiding
positioning issues and keeping the rectangle position synced even after scrolling
/ window resizing is definitely a challenge but we chose this way nonetheless.
The performance gain for the majority of the usage time outweighs the possible
errors in the corner cases, moreso since the eventual errors are not critical
and mostly remedied by further playback.

@@

It is clear that the ease of use is crucial in our case where the user is
supposed to perform a requiring, tedious task with repeated steps, especially
since it is our interest more than hers that she performs them. We compared our
setting with that of transcription apps in section~\ref{ssec:diff:trans},
pointing out lessons to learn. Let's now look at some specific points and their
actual (lack of) implementation.

@@

One of the features that Transcribe, the only commercial tool in our reference
list, offers is setting up keyboard shortcuts for common words. We haven't
implemented this because ideally, common words should be covered by the speech
recognition. However, it could be sensible to implement it anyway. The reason is
that a word can be very rare globally and thus poorly recognized by ASR but very
common in a specific passage. This particularly regards named entities.

@@

As stated above, when the user selects at least one character with the mouse,
the application enters the state of correcting the selected transcription padded
to whole words. In this mode, the transcription to correct is shown in a
textarea and the global playback controls are replaced by those that only allow
playback of audio corresponding to the selected transcription.

Once the user believes that the content of the textarea corresponds precisely
to the words uttered, she hits the {\em save} button or the \texttt{ctrl+enter}
keyboard shortcut. This starts an asynchronous HTTP request to the back-end,
where parametrized (MFCC) versions of the recordings are stored, along with the
new transcription and the time positions of the beginning and end of the
segment.

The server then cuts off the corresponding segment from the parametrized
recording, runs forced alignment on it with the provided transcription with a
threshold to reject bad matches. If the forced alignment fails, an error
response is sent back and the transcription is not merged into the original. In
the case of a success, the correction is merged on one hand on the server side
and pushed to a CDN, on the other hand it is merged into the transcription word
array in the JavaScript application. This redundancy warrants that we don't have
to reload the whole transcription every time a segment is corrected.

@@

Apart from this, the version of the transcription to the recording is updated.
This is because the transcriptions have a long cache time because normally, they
don't change at all. At the page load, the versions of all transcriptions are
loaded and used as cache busters. This enables us to use an external CDN and
cache effectively.

@@

We use React as the view library and Redux\cite{abramov2015redux} for state
management. The good thing about Redux is that it makes it easy to keep minimal
state as the single source of truth and everything that can be computed is
computed, while avoiding needless calculations. This is of course nothing new --
basically it is what we know from database design as the normal
representation.\cite{codd1970relational} It is the first time this approach
reached the web front-end in such degree of popularity though.

@@

We plan to focus on optimizing the app for wider audience. Experience confirms
that Mako\v{n}'s talks are of interest to some people, and our aim is to
remove as many obstacles as possible from potentially interested people reaching
the material. The benefit from technical point of view would be clear: A web app
for listening to recordings and correcting their transcription is nice but one
that's really easy to use and inviting to people to submit corrections is nicer.

@@

Another point of near-future endeavor is higher-level work with the contents. By
this we mean that we'd like to use both automatic processing methods and the
users to do semantic analysis of the talks: What topic is covered where? What
topics are covered at all? Which talks relate to which written works?, and
similar questions.

>>>>

The best widespread match to our task is that of creating an application for
transcribing speech recordings. Let us compare the two tasks, pointing out the
main points of difference. For reference, we take (1)
Transcriber\footnote{trans.sourceforge.net}, a classical open-source program
written in TCL, (2) oTranscribe\footnote{otranscribe.com}, a free modern
web-based transcription tool and (3) Transcribe\footnote{transcribe.wreally.com}
a commercial web-based transcription tool.

@@

Legend to Figure~\ref{fig:scn1lab}:
\begin{enumerate}
\item{
    Header with
    \begin{itemize}
    \item{app name linking to start page,}
    \item{about link,}
    \item{search field and}
    \item{username input field;}
    \end{itemize}
}
\item{Identifier of the recording;}
\item{Automatically transcribed segments in grey;}
\item{Manually transcribed segments in black;}
\item{Currently played-back word highlighted by yellow background;}
\item{Marked word highlighted in regent st. blue;}
\item{
    Marked word info:
    \begin{itemize}
    \item{
        occurrence: the word with contextual capitalization and
        punctuation as it appeared in the text (currently being edited as the
        selected initial letter reveals),
    }
    \item{form: normalized word form as it appears in the word list,}
    \item{pronunciation: Czech phonetic transcription of the word,}
    \item{
        position: time of the beginning of the word in seconds from the
        start of the recording;
    }
    \end{itemize}
}
\item{
    Tools for storing:
    \begin{itemize}
    \item{direct links to the audio files,}
    \item{selecting the whole transcription for easy pasting,}
    \item{storing the decoded recording in the browser's IndexedDB;}
    \end{itemize}
}
\item{Graphical equalizer for compensating narrow-band noise;}
\item{
    Audio playback controls:
    \begin{itemize}
    \item{play/pause button,}
    \item{current playback position,}
    \item{playback scrollbar,}
    \item{total recording length;}
    \end{itemize}
}
\item{Current position reflected in URL fragment.}
\end{enumerate}

@@

Legend to Figure~\ref{fig:scn2lab}:
\begin{enumerate}
\item{
    Selecting a text range with the mouse defines the segment the user is about
    to transcribe;
}
\item{
    The edit tool with
    \begin{itemize}
    \item{text area prefilled with the current transcription,}
    \item{playback button that plays the corresponding segment,}
    \item{save button and}
    \item{download-segment button, which initiates a file-save action for the
    audio segment corresponding the the selected text. The synthesis of the
    downloaded file takes place in the browser.}
    \end{itemize}
}
\end{enumerate}

@@

Although this may not seem like a big deal, it does affect the responsiveness
and memory footprint of the page.

@@

Wrapping the word would definetely be more robust and less error-prone but the
constant changes in the DOM during playback with possible frequent reflows speak
against it. Finding the exact position of each word and drawing a rectangle
precisely beneath it (beneath on the z-axis; over it in the x-y sense), avoiding
positioning issues and keeping the rectangle position synced even after scrolling
/ window resizing is definitely a challenge but we chose this way nonetheless.
The performance gain for the majority of the usage time outweighs the possible
errors in the corner cases, more so since the eventual errors are not critical
and mostly remedied by further playback.

@@

It is clear that the ease of use is crucial in our case where the user is
supposed to perform a requiring, tedious task with repeated steps, especially
since it is our interest more than hers that she performs them. We compared our
setting with that of transcription apps in section~\ref{ssec:diff:trans},
pointing out lessons to learn. Let us now look at some specific points and their
actual (lack of) implementation.

@@

One of the features that Transcribe, the only commercial tool in our reference
list, offers is setting up keyboard shortcuts for common words. We have not
implemented this because ideally, common words should be covered by the speech
recognition. However, it could be sensible to implement it anyway. The reason is
that a word can be very rare globally and thus poorly recognized by ASR but very
common in a specific passage. This particularly regards named entities.

@@

As stated above, when the user selects at least one character with the mouse,
the application enters the state of correcting the selected transcription padded
to whole words. In this mode, the transcription to correct is shown in a
text area and the global playback controls are replaced by those that only allow
playback of audio corresponding to the selected transcription.

Once the user believes that the content of the text area corresponds precisely
to the words uttered, she hits the {\em save} button or the \texttt{ctrl+enter}
keyboard shortcut. This starts an asynchronous HTTP request to the back-end,
where parametrized (MFCC) versions of the recordings are stored, along with the
new transcription and the time positions of the beginning and end of the
segment.

The server then cuts off the corresponding segment from the parametrized
recording, runs forced alignment on it with the provided transcription with a
threshold to reject bad matches. If the forced alignment fails, an error
response is sent back and the transcription is not merged into the original. In
the case of a success, the correction is merged on one hand on the server side
and pushed to a CDN, on the other hand it is merged into the transcription word
array in the JavaScript application. This redundancy warrants that we do not
have to reload the whole transcription every time a segment is corrected.

@@

Apart from this, the version of the transcription to the recording is updated.
This is because the transcriptions have a long cache time because normally, they
do not change at all. At the page load, the versions of all transcriptions are
loaded and used as cache busters. This enables us to use an external CDN and
cache effectively.

@@

We use React as the view library and Redux\cite{abramov2015redux} for state
management. The good thing about Redux is that it makes it easy to keep minimal
state as the single source of truth and everything that can be computed is
computed, while avoiding needless calculations. This is of course nothing new --
basically it is what we know from database design as the normal
representation\cite{codd1970relational}. It is the first time this approach
reached the web front-end in such degree of popularity though.

@@

We plan to focus on optimizing the app for wider audience. Experience confirms
that Mako\v{n}'s talks are of interest to some people, and our aim is to
remove as many obstacles as possible from potentially interested people reaching
the material. The benefit from technical point of view would be clear: A web app
for listening to recordings and correcting their transcription is nice but one
that is really easy to use and inviting to people to submit corrections is nicer.

@@

Another point of near-future endeavor is higher-level work with the contents. By
this we mean that we wouldd like to use both automatic processing methods and the
users to do semantic analysis of the talks: What topic is covered where? What
topics are covered at all? Which talks relate to which written works?, and
similar questions.
